---
title: "FA_Week1_Assignment"
author: "Zhilin Yang"
date: '2023-01-11'
output: html_document
---
Get Data
```{r}

library(quantmod)
# daily format
# use symbol name "EFFR" for business days
getSymbols("EFFR",src="FRED",from = as.Date("2022-01-01"), to = as.Date("2022-12-22"))
FedFunds<-EFFR
colnames(FedFunds)<-"FedFunds"

head(FedFunds)
```
```{r}
sp500 <- new.env()
getSymbols("^GSPC", env = sp500, src = "yahoo",from = as.Date("2022-01-01"), to = as.Date("2022-12-22"))
GSPC <- sp500$GSPC
GSPC1 <- get("GSPC", envir = sp500)
GSPC2 <- with(sp500, GSPC)
rm(GSPC1)
rm(GSPC2)
head(GSPC)
```
2.1 Calculate continuous daily excess returns of SP500 (“^GSPC”) for the period from 1/1/2022 until 12/22/2022 using overnight Fed Funds rates as risk-free rates.
```{r}
return = merge(GSPC,FedFunds)
return = na.omit(return)

#2.1 continuous daily excess return
return$daily_return = diff(log(GSPC$GSPC.Adjusted))
return$rf = log(1+return$FedFunds/360)
return$excess_return = return$daily_return-return$rf
head(return$excess_return)
```
2.2 Calculate average daily excess return, actual return of S&P 500 in 2022 per day, and average FedFund rate of return per day
```{r}
#2.2
#Actual return of SP 500
actual_return = diff(log(GSPC$GSPC.Adjusted))
head(actual_return)

#Average FedFunds rate of return
avg_fed_return = mean(return$FedFunds/360,na.rm= TRUE)
avg_fed_return


#Average Daily Excess Return
avg_daily_excess_return = mean((actual_return - log(1 + return$FedFunds/360)), na.rm = TRUE)
avg_daily_excess_return

```

3.1 Download from Oanda using method getFX() from library quantmode for the period from July 1, 2022 to December 22, 2022:
```{r}
#Get the Data
getFX("GBP/USD",from="2022-07-01",to="2022-12-22")
getFX("USD/JPY",from="2022-07-01",to="2022-12-22")
```
3.2 Calculate daily log returns of both exchange rates
```{r}
#Daily Log Returns of USDJPY
USDJPY_LR =  diff(log(USDJPY))
head(USDJPY_LR)


#Daily Log Returns of USDJPY
GBPUSD_LR =  diff(log(GBPUSD))
head(GBPUSD_LR)
```
3.3 Calculate sample min, mean, sd, skewness, kurtosis, max of log returns for both exchange rates

```{r}
library(fBasics)

basicStats(GBPUSD_LR)
#Therefore, the statistics for log returns of GBP/USD are min:-0.018921, max: 0.020607, sd:0.006120, skewness:0.235411, kurtosis:2.170017

basicStats(USDJPY_LR)
#Therefore, the statistics for log returns of USD/JPY are min:-0.029623, max: 0.015004, sd:0.006042, skewness:-1.387603, kurtosis:5.096345
```
3.4 Test hypothesis H0:μ=0 against alternative H0:μ≠0
```{r}
t.test(as.vector(USDJPY_LR), mu = 0)
t.test(as.vector(GBPUSD_LR), mu = 0)
#Since both of the p-values are much larger than 0.5, we fail to reject the null hypothesis. Therefore, we can believe that the mean of both exchange rate are equal to zero.
```


