---
title: "ts_final_project"
author: "Han Jiang"
date: "`r Sys.Date()`"
output: html_document
---

# MSCA 31006 Time Series Analysis and Forecasting

```{r}
# Set the new directory
path = '/Users/anthony/Desktop/MSCA Time Series/Assignment/Final Project'
setwd(path)
```

```{r}
library(tseries)
library(fpp)
library(forecast)
library(TSA)
library(ggplot2)
```

```{r}
library(stats)
library(ggplot2)
library(MuMIn)
library(MLmetrics)
library(tstools)
```

# Start Here

## Load

```{r}
file_path = "/Users/anthony/Desktop/MSCA Time Series/Assignment/Final Project/monthly_PJME.csv"
data <- read.csv(file_path)
```

## EDA

```{r}
head(data)
```

```{r}
electricity <- ts(data$monthly_sum, start = c(2002,1), frequency = 12)

# Make a time plot 
plot(electricity, main="Eletricity Consumption")
```
```{r}
tsdisplay(electricity)
```


## Decomposition

```{r}
plot(decompose(electricity, type="mult"))
```

```{r}
boxplot(electricity~cycle(electricity), xlab="Cycle (Year)", ylab="Megawatts(MW)", main="Energy Consumption for PJM")
```

```{r}
##Seasonal plot of electricity data
ggseasonplot(electricity,
            year.labels=TRUE)+
  scale_y_log10()+ # Put y axis on a logarithmic scale
  ylab("Electricity Consumption")+ # An alternate way to label Y axis
  ggtitle("Seasonal Plot of PJME Electricity Consumption, in Megawatts") # Add a title
```

```{r}
kpss.test(electricity)
```

```{r}
BoxCox.lambda(electricity)
```

```{r}
lambda <- BoxCox.lambda(electricity)

#electricity %>% BoxCox(lambda = lambda) 
```


```{r}
tsdisplay(diff(diff(electricity,lag = 12)),main='Monthly Average PJME Electricity Consumption (Seasonal Differencing)')
```

```{r}
kpss.test(diff(diff(electricity, lag = 6)))
```

```{r}
spectrum(electricity)
```

```{r}
periodogram(electricity)
```

## Train Test Split

```{r}
#pjm_train <- window(electricity, end = c(2017,7)) #end train in 2017.8
#pjm_test  <- window(electricity, start = c(2017,8)) #use last year of dataset as test

pjm_train <- window(electricity, end = c(2015,7)) #end train in 2017.8
pjm_test  <- window(electricity, start = c(2015,8)) #use last year of dataset as test
frequency(pjm_train) 
```

```{r}
#cycle(pjm_test) 
cycle(electricity) 
```

## Dynamic Harmonic Regression

```{r}
temp <- periodogram(electricity)
```

```{r}
spec_p <- matrix(round(temp$spec/1e5, 2))
freq_p <- matrix(temp$freq)
cbind(spec_p, freq_p) # major spikes at 0.005, 0.085, 0.165, 0.170, 0.250
```

```{r}
library(gridExtra)
```

```{r}
plots <- list()
for (i in seq(6)) {
  fit <- auto.arima(pjm_train, xreg = fourier(pjm_train, K = i),
    seasonal = FALSE, lambda = 0)
  plots[[i]] <- autoplot(forecast(fit,
      xreg=fourier(pjm_train, K=i, h=36))) +
    xlab(paste("K=",i,"   AICC=",round(fit[["aicc"]],2))) +
    ylab("")+
    theme_grey(base_size = 7)  # Adjust the base font size
}
gridExtra::grid.arrange(
  plots[[1]],plots[[2]],plots[[3]],
  plots[[4]],plots[[5]],plots[[6]], nrow=3)
```

### Forecast with Auto ARIMA

We create a regression model using a Fourier transformation (K=2) as the predictor, and Arima errors. This results in an ARIMA(0,1,2)(0,0,2)[12] model. The residuals are stationary and relatively normally distributed, signaling that they are white noise (p=0.09553).

```{r}
DHR <-  auto.arima(pjm_train, xreg=fourier(pjm_train, K=2)) 
summary(DHR)
```

```{r}
checkresiduals(DHR)
```

```{r}
DHR1_fcast <- forecast(DHR, h=12, xreg=fourier(pjm_train, K=2, h=36))
plot(DHR1_fcast, pjm_test)
```

```{r}
#tsplot(cbind(pjm_test, DHR1_fcast$mean), plot_title = "Actual vs. Predicted", auto_legend=TRUE)
```

```{r}
ts.plot(pjm_test, ts(DHR1_fcast$mean, start=c(2015,8), frequency=12), gpars = list(col = c("black", "blue")),
        xlab = "Date", ylab = "Value",
        main = "Actual vs DHR Prediction", col.lab = "black", col.main = "black", col.axis = "black")

legend("topleft", legend = c("Actual", "Prediction"), col = c("black", "blue"), lty = 1, lwd = 2)
```

```{r}
MAE(DHR1_fcast$mean, pjm_test)
```

```{r}
RMSE(DHR1_fcast$mean, pjm_test)
```

### Forecast with ARIMA

```{r}
# Fit ARIMA(2,1,1) with DHR using Fourier terms
DHR.2 = Arima(pjm_train, order = c(2, 0, 0), seasonal = list(order = c(2, 0, 0), period = 12),
                   xreg = fourier(pjm_train, K = 2))

# Display summary of the DHR_ARIMA model
summary(DHR.2)
```

```{r}
checkresiduals(DHR.2)
```

```{r}
DHR2_fcast <- forecast(DHR.2, h=36, xreg=fourier(pjm_train, K=2, h=36))
plot(DHR2_fcast, pjm_test)
```

```{r}
ts.plot(pjm_test, ts(DHR2_fcast$mean, start=c(2015,8), end=c(2018,7), frequency = 12), gpars = list(col = c("black", "blue")),
        xlab = "Date", ylab = "Value",
        main = "Actual vs DHR Prediction", col.lab = "black", col.main = "black", col.axis = "black")

legend("topleft", legend = c("Actual", "Prediction"), col = c("black", "blue"), lty = 1, lwd = 2)
```

```{r}
MAE(DHR2_fcast$mean, pjm_test)
```

```{r}
RMSE(DHR2_fcast$mean, pjm_test)
```
